\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}

% Setting the page margins to 1 inch all around
\geometry{a4paper, margin=1in}
\pagestyle{empty}

\title{Detailed AI Project Descriptions}
\author{Saurabh Nandedkar}
\date{}

\begin{document}

\maketitle

\section*{Projects Overview}

\subsection*{AI Retrieval-Augmented Generation Chatbot for Trading Platform}
\textbf{Role:} Lead Developer \\
\textbf{Technologies:} FastAPI, React, OpenAI TPU, PostgreSQL \\
\textbf{Description:} Led development of an AI-driven RAG chatbot, utilizing OpenAI TPUs for model hosting, enabling real-time interaction and data processing. Integrated with PostgreSQL for robust data management, handling datasets from financial markets and real-time news feeds. \\
\textbf{Functionality:} Supports decision-making by providing market insights within the trading platform. Enhances administrative functions with automated responses to market and regulatory changes.

\subsection*{Tax Helper RAG Chatbot}
\textbf{Role:} AI Solutions Architect \\
\textbf{Technologies:} Milvus, Custom Database \\
\textbf{Description:} Designed a RAG chatbot to assist users with tax regulation queries, utilizing Milvus for vector data management and a custom database for fetching real-time tax data. \\
\textbf{Functionality:} Automates responses to queries, improving compliance and providing tailored tax advice, thus simplifying user interaction with complex tax regulations.

\subsection*{Private Custom LLM Development for Semiconductor Tool}
\textbf{Role:} Solutions Engineer \\
\textbf{Technologies:} llama.cpp, instructor \\
\textbf{Description:} Developed a custom LLM for processing semiconductor manufacturing data, enhancing design and production decision-making capabilities. \\
\textbf{Functionality:} Allows for more accurate data analysis and faster response to design changes, supporting critical semiconductor production tasks.

\subsection*{On-Device Local LLM for Education Systems}
\textbf{Role:} Project Lead \\
\textbf{Technologies:} llama.cpp, React Native, RxDB \\
\textbf{Description:} Developing an on-device local LLM-based RAG system for educational applications, running entirely on-device within a React Native environment, using RxDB for data management. \\
\textbf{Functionality:} Delivers personalized educational content without internet dependency, enhancing engagement and accessibility.

\end{document}
