\documentclass[a4paper,9pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{multicol}

\titleformat{\section}{\large\bfseries}{}{0em}{}
\titleformat{\subsection}{\small\bfseries}{}{0em}{}
\titleformat{\subsubsection}{\footnotesize\bfseries}{}{0em}{}
\titlespacing{\section}{0pt}{*0.5}{*0.5}
\titlespacing{\subsection}{0pt}{*0.5}{*0.5}
\titlespacing{\subsubsection}{0pt}{*0.5}{*0.5}

\setlist[itemize]{leftmargin=*, itemsep=0pt, topsep=0pt}

\begin{document}

\begin{center}
    \textbf{\LARGE SAURABH NANDEDKAR} \\
    \vspace{1pt}
    \href{mailto:saurabhnandedkar25@gmail.com}{saurabhnandedkar25@gmail.com} $\vert$\href{https://saurabhn.com}{saurabhn.com} $\vert$ \href{tel:+919892356631}{+91-9892356631}
 $\vert$ \href{https://github.com/EXTREMOPHILARUM}{GitHub} $\vert$ \href{https://linkedin.com/in/extremophilarum}{LinkedIn} 
\end{center}

\vspace{3pt}

\section*{PROFESSIONAL SUMMARY}

Results-driven Cloud Architect with over 5 years of experience in cloud infrastructure, DevOps, and security engineering. Proven track record of revamping outdated systems, driving DevOps transformations, and implementing robust security solutions. Strong leadership skills in mentoring junior engineers and spearheading complex cloud initiatives. Seeking to leverage technical expertise and leadership to execute meaningful initiatives in a dynamic organization.

\section*{WORK EXPERIENCE}

\subsection*{Turing, Cloud Architect, Remote (Apr. 2023 - Current)}
\begin{itemize}
    \item Spearheaded the overhaul of legacy systems, achieving a 30\% increase in performance metrics while aligning with evolving business needs, leading to a 20\% reduction in operational costs.
    \item Led the migration to a Kubernetes-based infrastructure, enhancing scalability by 40\%, resilience by 35\%, and optimizing resource usage, resulting in a 25\% cost efficiency improvement.
    \item Implemented advanced Cloud Security Posture Management (CSPM) solutions, bolstering security and compliance across multiple cloud environments, reducing security incidents by 50\%.
\end{itemize}

\subsection*{Prismberry Technologies, Software and DevOps Engineer, Delhi (Nov. 2021 - Apr. 2023)}
\begin{itemize}
    \item Drove DevOps transformation for a healthcare marketplace using Terraform and Kubernetes, reducing repetitive infrastructure operations by 50\% through automation, which accelerated deployment frequency by 60\%.
    \item Delivered backend services for a GIS-based maritime tracking system, leveraging AIS data analytics to enhance real-time accuracy by 45\% and improving system response time by 30\%.
    \item Mentored and developed 5 junior engineers, fostering a learning-focused culture within the team, which improved team productivity by 20\%.
\end{itemize}

\subsection*{Safe Security, DevSecOps Engineer & security analyst, Mumbai (Jan. 2020 - Nov. 2021)}
\begin{itemize}
    \item Engineered automated security workflows for critical CRQ platforms, enabling continuous assessment and reducing vulnerabilities by 40\%, leading to a 30\% reduction in security breaches.
    \item Conducted detailed source code analysis across various programming languages, significantly strengthening application defenses and reducing code vulnerabilities by 50\%.
    \item Constructed an automated web application scanning system, enhancing security effectiveness by 35\% and limiting manual intervention by 60\%.
    \item Performed in-depth security evaluations and implemented mitigation strategies, reinforcing the overall security stance and reducing critical vulnerabilities by 25\%.
    \item Promoted security best practices, enhancing the security culture across teams and reducing incidents by 20\%.
\end{itemize}

\subsection*{Freelance Engineer, Delhi (Jan. 2019 - Current)}
\begin{itemize}
    \item Led development of an AI-driven RAG chatbot for trading platforms using FastAPI and OpenAI TPUs, enabling real-time market insights and automated responses to regulatory changes.
    \item Designed a tax regulation RAG chatbot utilizing Milvus for vector data management, automating responses and improving compliance efficiency.
    \item Developed custom VSCode SaaS environment with LLM support for SystemRDL and hardware description languages, enabling collaborative development and AI-assisted code generation.
    \item Created on-device local LLM educational system with React Native and RxDB, delivering personalized content without internet dependency.
    \item Engineered high-availability email infrastructure and internal search engine for air-gapped environments, achieving 99.9\% uptime.
    \item Managed Kubernetes deployments for ElasticSearch clusters and implemented automated site indexing, reducing manual effort by 40\%.
\end{itemize}

\section*{SKILLS}

\begin{multicols}{2}
\begin{itemize}[leftmargin=*]
    \item \textbf{Programming Languages}: Python, JavaScript, Google Apps Script
    \item \textbf{Backend Frameworks}: FastAPI, Flask, Django, Tornado
    \item \textbf{Frontend}: React, React Native
    \item \textbf{DevOps Tools}: Docker, Jenkins, GitHub Actions, Ansible, Terraform, Kubernetes
    \item \textbf{Cloud Services}: AWS, GCP, Azure, Cloudflare
\end{itemize}
\end{multicols}

\section*{EDUCATION}

\subsection*{National Institute of Technology, Kurukshetra (July 2017 - May 2021)}
\textit{B. Tech in Computer Engineering}

\section*{CERTIFICATIONS}
\subsection*{Google Cloud Professional Cloud Architect Certification (GCP) (Apr. 2023)}

\section*{PROJECTS}

\subsection*{Confidential Trading Platform (Apr. 2023 - Current)}
\begin{itemize}
    \item Led the design of a high-throughput trading platform across AWS, GCP, and Azure, handling over 4,000 transactions per second, resulting in a 20\% increase in transaction efficiency.
    \item Utilized Terraform for automated multi-cloud provisioning, resulting in a 30\% reduction in manual errors and deployment time.
    \item Maintained cloud operations through automated oversight and scaling, achieving 99.9\% uptime and reducing operational overhead by 25\%.
\end{itemize}

\subsection*{Flipkart Health Plus (Jan. 2022 - Apr. 2023)}
\begin{itemize}
    \item Spearheaded cloud infrastructure initiatives using Kubernetes and Terraform on GCP and AWS, enhancing system efficiency by 25\% and reducing deployment time by 40\%.
    \item Migrated AWS resources to GCP, resulting in 20\% cost savings and reducing deployment time by 40\%.
    \item Designed automation scripts to streamline deployment, decreasing manual efforts by 50\% and reducing error rates by 30\%.
\end{itemize}

\subsection*{Password Manager (Jan. 2019 - Apr. 2023)}
\begin{itemize}
    \item Engineered a multi-tenant password management system with Flask and WebSockets, ensuring isolated data access and improving security by 30\%.
    \item Designed a secure backend and a cross-browser extension, enabling seamless real-time password management, which reduced response times by 20\%.
    \item Designed WebSocket-based instant password access, improving user experience across platforms and increasing usage by 25\%.
\end{itemize}

\subsection*{AI Trading RAG Chatbot (Apr. 2023 - Current)}
\begin{itemize}
    \item Architected an AI-driven RAG chatbot using FastAPI and React, integrating OpenAI TPUs for real-time market data processing.
    \item Implemented PostgreSQL for robust data management, handling complex datasets from financial markets and news feeds.
    \item Enhanced administrative efficiency through automated responses to market changes and regulatory updates.
\end{itemize}

\subsection*{Tax Helper RAG System (Jan. 2023 - Mar. 2023)}
\begin{itemize}
    \item Designed and implemented a RAG chatbot using Milvus for vector data management, streamlining tax regulation queries.
    \item Built custom database integration for real-time tax data retrieval, improving compliance and user interaction.
    \item Automated response system reduced query resolution time by 60\% while maintaining accuracy.
\end{itemize}

\subsection*{VSCode SaaS Development Environment (Oct. 2022 - Dec. 2022)}
\begin{itemize}
    \item Engineered a cloud-based VSCode environment with real-time code collaboration capabilities and LLM integration.
    \item Implemented instructor-based fine-tuning to enhance model accuracy for specific manufacturing contexts.
    \item Achieved 40\% faster response to design changes while maintaining high accuracy in predictions.
\end{itemize}

\subsection*{Educational Local LLM System (Jul. 2022 - Sep. 2022)}
\begin{itemize}
    \item Built on-device LLM-based RAG system using React Native and RxDB for offline educational content delivery.
    \item Implemented efficient data synchronization and caching strategies for optimal performance.
    \item Enhanced student engagement through personalized learning paths and instant feedback mechanisms.
\end{itemize}

\end{document}
